The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-08-13 paper/ms.tex
6 cosmic variance graphs

\subsection{Bouwens et al. 2015}
\citet{Bouwens15} presented results from a compilation of
observations taken with the Advanced Camera for Surveys (ACS) and
near-infrared Wide Field Camera 3 (WFC3/IR) since 2002 through 2012. 
The study inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS.
%The information in that study comes from the ACS and WFC3/IR using the
%filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
%$J{125}$,  $JH_{140}$ and $H_{160}$.

@@

They performed otical observations with MegaCam.
Their main selection criteria was that all objects must be brighter
than magnitude $z' = 25.3$. 
The final  number of LBGs founded was 40. 
Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view,

@@

\begin{figure}
\epsscale{1.00} 
\plotone{fig/observational_data.pdf}
\caption{Observational data from \cite{Bouwens15,McLure09}and \cite{Willott13}.}
\label{graph_observational_data}
\end{figure}

@@

>>>>

\subsection{Bouwens et al. 2015}
\citet{Bouwens15} presented results from a compilation of
observations taken with the Advanced Camera for Surveys (ACS) and
near-infrared Wide Field Camera 3 (WFC3/IR) since 2002 through 2012. 
The survey inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS.
%The information in that study comes from the ACS and WFC3/IR using the
%filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
%$J{125}$,  $JH_{140}$ and $H_{160}$.

@@

They performed optical observations with MegaCam.
Their main selection criteria was that all objects must be brighter
than magnitude $z' = 25.3$. 
The final  number of LBGs founded was 40. 
Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view,

@@

\begin{figure}
\epsscale{1.00} 
\plotone{fig/observational_data.pdf}
\caption{Observational data from \cite{Bouwens15,Finkelstein14,McLure09}and \cite{Willott13}.}
\label{graph_observational_data}
\end{figure}

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD2_CosmicVar1_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Bouwens data in the dust
 attenuation model.}
\label{fig:OD2_CosmicVar1_w_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_CosmicVar1_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with McLure data in the dust
 attenuation model.}
\label{fig:OD3_CosmicVar1_w_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD4_CosmicVar1_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the dust
 attenuation model.}
\label{fig:OD4_CosmicVar1_w_dust}
\end{figure}
